---
title: "Immunoassay Reagent Lot Validation"
output: 
    pdf_document:
        keep_tex: true
        includes:
            in_header: header.tex
        fig_caption: yes
        number_sections: yes
fontsize: 11pt 
geometry: margin=1in
params:
    analyte: 
        label: "Analyte:"
        value: "TSH"
        input: select
        choices: [TSH, N17P, IRT]
    data: 
        label: "Input dataset:"
        value: TSH_lot_validation_2017-04-05.xls
        input: text
    recommendation: 
        label: "Recommendation:"
        value: ""
        input: select
        choices: [accepted, not accepted]
---

\centering

\includegraphics[width = 60mm]{./figures/NSO_logo.pdf}

\raggedright
\tableofcontents 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.width=6)
```

```{r} 
library("dplyr")
library("magrittr")
library("ggplot2")
library("tidyr")
library("mcr")
library("readxl")
library("pander")
library("qcc")

## set analyte_info dependant on analyte
info <- switch(params$analyte,
               "TSH" = list(units = "mIU/L", threshold = 17, upper = 40),
               "N17P" = list(units = "nmol/L", threshold = 38, upper = 60),
               "IRT" = list(units = "ng/ml", threshold = 48, upper = 100))
```

# Recommendation 

The `r params$analyte` reagent lot is `r params$recommendation` for use.

# Methods
- Three `r params$analyte` reagent validation plates were run on three consecutive days.
- The data source used in this analysis is: `r params$data`

# Validation Analysis

Deming regression was used to assess the agreement between the `r params$analyte` kit
lots (figures \ref{fig:dem}, \ref{fig:diff}).


## Data Summary

```{r}
comp <- read_xls(params$data, sheet = 2)
## until pander bug is fixed
##pander:pander(summary(comp[, c("old", "new")]))
```

```{r, fig.cap="\\label{fig:dens}Density plot for the reagent lot comparison"}

  comp %>%
      gather(lot, result, old:new) %>%
      ggplot(aes(result, fill = lot)) +
      geom_density(alpha = 0.5) +
      facet_grid(.~ day) +
      xlab(paste(params$analyte, info$units)) +
      scale_fill_discrete(name = "Lot")
    
  # labs(title = "Density plot for the TSH reagent lot comparison")
```

## Paired T-test

```{r}
pander::pander(t.test(comp$old, comp$new, paired = TRUE))
```

## Regression Analysis

```{r, fig.cap="\\label{fig:dem}Deming regression"}
comp.deming <- mcreg(x = comp$old, y =comp$new, error.ratio = 1, alpha = 0.05,
                     mref.name = "Old", mtest.name = "New", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(comp.deming, x.lab = "Old", y.lab = "New", main=paste(params$analyte, "Reagent Lot Comparision"))
```


The data set was filtered to remove values greater than `r info$upper`.

```{r, fig.cap="\\label{fig:dem}Filtered Deming regression"}
trim <- comp %>%
     filter(old < info$upper & new < info$upper)

    trim.deming <- mcreg(x = trim$old, y =trim$new, error.ratio = 1, alpha = 0.05,
                   mref.name = "Old", mtest.name = "New", sample.names = NULL,
                   method.reg = "Deming", method.ci = "bootstrap",
                   method.bootstrap.ci = "BCa",
                   nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                   threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

  plot(trim.deming, x.lab = "Old", y.lab = "New", main=paste(params$analyte, "Filtered Reagent Lot Comparision"))
```


```{r} 
pander::pander(trim.deming@para, caption = "\\label{tab:para}Regression Parameters")
``` 


```{r,fig.cap="\\label{fig:diff}Difference Plot"}
plotDifference(trim.deming, main= paste(params$analyte, "Reagent Lot Comparision"))
```

## Screening Thresholds
 
The regression parameters (table \ref{tab:para}) were used to determine the effect of this reagent lot on the screening threshold.

```{r}
intercept <- trim.deming@para[1,1] # intercept
slope <- trim.deming@para[2,1] # slope

reg <- function(m,x,b){
      y <- m * x + b
      return(round(y, digits = 3))
}
```
- A result of `r reg(slope, info$threshold, intercept)` `r info$units` with this `r params$analyte` reagent lot is equivalent to a value at the screening threshold (`r info$threshold` `r info$units`) with the current reagent lot.


## Quality Control Material
- Shewhart Xbar charts illustrate QC performance during the validation phase
  (Figures \ref{fig:qc1}, \ref{fig:qc2} and \ref{fig:qc3}).


```{r, fig.cap="\\label{fig:qc1} Xbar.one plot of QC Level 1 validation data"}
qc <- read_excel(params$data, sheet = 3)
qc1 <- qcc(qc$QC1, type = "xbar.one",  nsigmas = 3, std.dev = "SD", chart.all = FALSE, title = "QC 1", ylab = "ng/ml", xlab = "run")
```

```{r, fig.cap="\\label{fig:qc2} Xbar.one plot of QC Level 2 validation data"}
qc2 <- qcc(qc$QC2, type = "xbar.one", nsigmas = 3, std.dev = "SD", chart.all = FALSE, title = "QC 2", ylab = "ng/ml", xlab = "run")
```

```{r,fig.cap="\\label{fig:qc3} Xbar.one plot of QC Level 3 validation data"}
qc3 <- qcc(qc$QC3, type = "xbar.one", nsigmas = 3, std.dev = "SD", chart.all = FALSE, title = "QC 3", ylab = "ng/ml", xlab = "run")
```
